A practical guide to Digital Micro-mirror Devices (DMDs) for wavefront shaping

### 2023-11-16 paper/main.tex
remove ALP4lib part
Add outline

Third-party companies have developed kits tailored for research applications,
which include a DMD, a control board, and a software interface.
Specifically, Vialux devices~\cite{vialux} offer an FPGA board that enables high-speed modulation
by allowing frames to be stored in the device's memory~\cite{hofling2004alp}.
However, standard Texas Instruments video projector evaluation modules can also be repurposed into wavefront shaping devices~\cite{Cox2021converting},
though at a compromised modulation speed.
These systems can further be converted into phase or complex field modulators.
This is typically achieved by encoding the optical phase into
the spatial displacement of binary spatial fringes displayed on the DMD,
followed by filtering the high spatial frequencies in the Fourier plane~\cite{lee1979binary}.
Such a configuration permits multi-level complex modulation but sacrifices spatial resolution.
The implementation and performance of such systems are explored in a separate tutorial~\cite{Gutierrez2024DMD}
and will not be elaborated upon here.
For the remainder of this paper, it will be assumed that the DMD is used for complex modulation via such a method.
While the present tutorial is not constrained to any specific device,
the software section will predominantly focus on the Vialux control board.
In the first part....\\

>>>>

Third-party companies have developed kits tailored for research applications,
which include a DMD, a control board, and a software interface.
Specifically, Vialux devices~\cite{vialux} offer an FPGA board that enables high-speed modulation
by allowing frames to be stored in the device's memory~\cite{hofling2004alp}.
However, standard Texas Instruments video projector evaluation modules can also be repurposed into wavefront shaping devices~\cite{Cox2021converting},
though at a compromised modulation speed.
These systems can further be converted into phase or complex field modulators.
This is typically achieved by encoding the optical phase into
the spatial displacement of binary spatial fringes displayed on the DMD,
followed by filtering the high spatial frequencies in the Fourier plane~\cite{lee1979binary}.
Such a configuration permits multi-level complex modulation but sacrifices spatial resolution.
The implementation and performance of such systems are explored in a separate tutorial~\cite{Gutierrez2024DMD}
and will not be elaborated upon here.
For the remainder of this paper, it will be assumed that the DMD is used for complex modulation via such a method.\\
% While the present tutorial is not constrained to any specific device,
% the software section will predominantly focus on the Vialux control board.
In the first part, we present the diffraction properties of a DMD
and detail how they may affect the efficiency of the system.
We provide a simple criteria for choosing the correct DMD parameters for a given excitation wavelenght.
In the second part, we detail the aberration effects induced but the non-flatness of the DMD surface.
We show how to simply characterize and compensate this effect.
In the third section, we describe the effect of mechanmical vibrations induced by the cooling system of the DMD.
Finally, we show how the thermalization of the DMD chip can induce fluctuations of the DMD response over time.
